---
title: "B. Methods sna - annual observation time & integration correlations"
author: "Nic TG"
date: "5/8/2021"
output: html_document
---

```{r setup, include=FALSE, messages = FALSE}
library(tidyverse)
library(ggcorrplot)
library(corrplot)
select<- dplyr::select

# for total possible observation time
load("data/total possible focal and possible party membership.Rdata", verbose = T)

# for directed degree n strength
load("data/sna dataframe - unweighted measures, individual sna measure for each year, network sex, & behavior.Rdata", verbose = TRUE)
# for all other measures
load("data/sna dataframe - weighted measures, individual sna measure for each year, network sex, & behavior.Rdata", verbose = TRUE)

colors <- colorRampPalette(c("blue", "white", "red"))(200)

```
```{r setup - create sna dfs with focal and party membership hours, include = FALSE}
library(ggcorrplot)

# grooming deg in out
dir_uw_df_mixed <- dir_sna_measure_df_uw %>%
  filter(network_sex == "any_combo") %>%
  left_join(.,total_poss_foc_n_party, by = c("chimp_id" = "ID1","year", "sex")) %>%
  select(chimp_id, sex, year, deg_in, deg_out, focal_hours, party_hours) 
nrow(dir_uw_df_mixed) #200
apply(dir_uw_df_mixed, 2, function(x) sum(is.na(x))) # all 0

dir_uw_df_same <- dir_sna_measure_df_uw %>%
  filter(network_sex != "any_combo") %>%
  left_join(.,total_poss_foc_n_party, by = c("chimp_id" = "ID1","year", "sex")) %>%
  select(chimp_id, sex, year, deg_in, deg_out, focal_hours, party_hours) 
nrow(dir_uw_df_same) #200
apply(dir_uw_df_same, 2, function(x) sum(is.na(x))) # all 0


# grooming st in out
dir_w_df_mixed <- dir_sna_measure_df_w %>%
  filter(network_sex == "any_combo") %>%
  left_join(.,total_poss_foc_n_party, by = c("chimp_id" = "ID1","year", "sex")) %>%
  select(chimp_id, sex, year, deg_in, deg_out, focal_hours, party_hours)
nrow(dir_w_df_mixed) #200
apply(dir_w_df_mixed, 2, function(x) sum(is.na(x))) # all 0

dir_w_df_same <- dir_sna_measure_df_w %>%
  filter(network_sex != "any_combo") %>%
  left_join(.,total_poss_foc_n_party, by = c("chimp_id" = "ID1","year", "sex")) %>%
  select(chimp_id, sex, year, deg_in, deg_out, focal_hours, party_hours)
nrow(dir_w_df_same) #200
apply(dir_w_df_same, 2, function(x) sum(is.na(x))) # all 0

# grooming bt, trans, ec
other_gm_df_mixed <- all_sna_measure_df_w %>%
  filter(behavior == "total_grooming" & network_sex == "any_combo") %>%
  left_join(.,total_poss_foc_n_party, by = c("chimp_id" = "ID1","year", "sex")) %>%
  select(chimp_id, sex, year, bt, trans, ec, focal_hours, party_hours) 
nrow(other_gm_df_mixed) #200
apply(other_gm_df_mixed, 2, function(x) sum(is.na(x))) # all 0

other_gm_df_same<- all_sna_measure_df_w %>%
  filter(behavior == "total_grooming" & network_sex != "any_combo") %>%
  left_join(.,total_poss_foc_n_party, by = c("chimp_id" = "ID1","year", "sex")) %>%
  select(chimp_id, sex, year, bt, trans, ec, focal_hours, party_hours) 
nrow(other_gm_df_same) #200
apply(other_gm_df_same, 2, function(x) sum(is.na(x))) # all 0

# prox st, bt, trans, ec
all_prox_df_mixed <- all_sna_measure_df_w %>%
  filter(behavior == "prox" & network_sex == "any_combo") %>%
  left_join(.,total_poss_foc_n_party, by = c("chimp_id" = "ID1","year", "sex")) %>%
  select(chimp_id, sex, year, deg, bt, trans, ec, focal_hours, party_hours) 
nrow(all_prox_df_mixed) #200
apply(all_prox_df_mixed, 2, function(x) sum(is.na(x))) # all 0

 all_prox_df_same<- all_sna_measure_df_w %>%
  filter(behavior == "prox" & network_sex != "any_combo") %>%
  left_join(.,total_poss_foc_n_party, by = c("chimp_id" = "ID1","year", "sex")) %>%
  select(chimp_id, sex, year, deg, bt, trans, ec, focal_hours, party_hours) 
nrow(all_prox_df_same) #200
apply(all_prox_df_same, 2, function(x) sum(is.na(x))) # all 0

```
```{r setup - create sna and obs df, include=FALSE}
sna_obs <- all_sna_measure_df_w %>%
  distinct(chimp_id, year) %>%
  left_join(total_poss_foc_n_party, by = c("chimp_id" = "ID1", "year"))
  
```


## Observation time
What were the mean and spread of focal and party membership hours...



By year?
```{r average number of focal and party hours per chimp year, message = FALSE, echo=FALSE,warning=FALSE}
annual_obs <- sna_obs %>%
  group_by(year) %>%
  summarise(avg_focal = mean(focal_hours), sd_focal = sd(focal_hours), min_focal = min(focal_hours), max_focal = max(focal_hours), avg_party_memb = mean(party_hours), sd_party = sd(party_hours), min_party = min(party_hours), max_party = max(party_hours)) %>%
  ungroup() %>%
  mutate_if(is.numeric, round, 1) %>%
  unite(col = "Mean ± sd focal hours per subject", c("avg_focal", "sd_focal"), sep = " ± ") %>%
  unite(col = "Mean ± sd party hours per subject", c("avg_party_memb", "sd_party"), sep = " ± ") %>%
select(year, starts_with("Mean"), everything())

annual_obs_sex <- sna_obs %>%
  group_by(year, sex) %>%
  summarise(avg_focal = mean(focal_hours), sd_focal = sd(focal_hours), min_focal = min(focal_hours), max_focal = max(focal_hours), avg_party_memb = mean(party_hours), sd_party = sd(party_hours), min_party = min(party_hours), max_party = max(party_hours)) %>%
  ungroup() %>%
  mutate_if(is.numeric, round, 1) %>%
  unite(col = "Mean ± sd focal hours per subject", c("avg_focal", "sd_focal"), sep = " ± ") %>%
  unite(col = "Mean ± sd party hours per subject", c("avg_party_memb", "sd_party"), sep = " ± ") %>%
select(year, sex, starts_with("Mean"))


annual_obs 
annual_obs_sex
#write.table(annual_obs_sex, file = "results/tables/annual avg focal observations.txt", sep = "/", row.name = F, quote = F)
```

Across all years?
```{r average across all chimp years, message = FALSE, echo=FALSE,warning=FALSE}
sna_obs %>% 
  summarise(avg_focal = mean(focal_hours), sd_focal = sd(focal_hours), min_focal = min(focal_hours), max_focal = max(focal_hours), avg_party_memb = mean(party_hours), sd_party = sd(party_hours), min_party = min(party_hours), max_party = max(party_hours)) %>%
  select(starts_with("avg"), starts_with("sd"), everything()) %>%
  ungroup()
```

Across all years by sex?
```{r average across all chimp years by sex, message = FALSE, echo=FALSE,warning=FALSE}
sna_obs %>% 
  group_by(sex) %>%
  summarise(avg_focal = mean(focal_hours), sd_focal = sd(focal_hours), min_focal = min(focal_hours), max_focal = max(focal_hours), avg_party_memb = mean(party_hours), sd_party = sd(party_hours), min_party = min(party_hours), max_party = max(party_hours)) %>%
  select(starts_with("avg"), starts_with("sd"), everything()) %>%
  ungroup()
```


## Observation time and integration
Exploring how observation time, as focal or in parties, corresponds with integration measures.


### Across all subjects

Directed Grooming
```{r - directed grooming deg, fig.keep = 'last', echo=FALSE, warning=FALSE}

layout(t(1:2))

# gm deg in out - mixed
stat1 <- dir_uw_df_mixed %>%
  select(-chimp_id, -year, -sex) %>%
  cor(.,  method = "spearman", use = "pairwise.complete.obs") 
pmat1 <- dir_uw_df_mixed %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(.,  method = "spearman", use = "pairwise.complete.obs") %>% .[[1]] 

corrplot(stat1, p.mat= pmat1, sig.level = c(.001, .01, .05),insig = "label_sig",         method="color",type = "upper", col = colors, title = "Total grooming mixed")

# gm deg in out - same
stat2 <- dir_uw_df_same %>%
  select(-chimp_id, -year, -sex) %>%
  cor(.,  method = "spearman", use = "pairwise.complete.obs") 
pmat2 <- dir_uw_df_same %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(.,  method = "spearman", use = "pairwise.complete.obs") %>% .[[1]] 

colors <- colorRampPalette(c("blue", "white", "red"))(200)

corrplot(stat2, p.mat= pmat2, sig.level = c(.001, .01, .05),insig = "label_sig",         method="color",type = "upper", col = colors, title = "Total grooming same")


```

```{r - directed grooming strength, fig.keep = 'last',echo=FALSE, warning=FALSE}
layout(t(1:2))

# gm st in out - mixed
stat3 <- dir_w_df_mixed %>%
  select(-chimp_id, -year, -sex) %>%
  cor(.,  method = "spearman", use = "pairwise.complete.obs") 
pmat3 <- dir_w_df_mixed %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(.,  method = "spearman", use = "pairwise.complete.obs") %>% .[[1]]  

colors <- colorRampPalette(c("blue", "white", "red"))(200)

corrplot(stat3, p.mat= pmat3, sig.level = c(.001, .01, .05),insig = "label_sig",         method="color",type = "lower", col = colors, title = "Total grooming mixed")

# gm st in out - same
stat4 <- dir_w_df_same %>%
  select(-chimp_id, -year, -sex) %>%
  cor(.,  method = "spearman", use = "pairwise.complete.obs") 
pmat4 <- dir_w_df_same %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(.,  method = "spearman", use = "pairwise.complete.obs") %>% .[[1]] 

colors <- colorRampPalette(c("blue", "white", "red"))(200)

corrplot(stat4, p.mat= pmat4, sig.level = c(.001, .01, .05),insig = "label_sig",         method="color",type = "lower", col = colors,  title = "Total grooming same")

```

Total Grooming
```{r - total grooming bt trans ec,  fig.keep = 'last', echo=FALSE, warning=FALSE}
layout(t(1:2))

# gm bt trans ec - mixed
stat5 <- other_gm_df_mixed %>%
  select(-chimp_id, -year, -sex) %>%
  cor(.,  method = "spearman", use = "pairwise.complete.obs") 
pmat5 <- other_gm_df_mixed %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(.,  method = "spearman", use = "pairwise.complete.obs") %>% .[[1]] 

colors <- colorRampPalette(c("blue", "white", "red"))(200)

corrplot(stat5, p.mat= pmat5, sig.level = c(.001, .01, .05),insig = "label_sig",         method="color",type = "lower", col = colors, title = "Total grooming mixed")


# gm bt trans ec - same
stat6 <- other_gm_df_same %>%
  select(-chimp_id, -year, -sex) %>%
  cor(.,  method = "spearman", use = "pairwise.complete.obs") 
pmat6 <- other_gm_df_same %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(.,  method = "spearman", use = "pairwise.complete.obs") %>% .[[1]] 

colors <- colorRampPalette(c("blue", "white", "red"))(200)

corrplot(stat6, p.mat= pmat6, sig.level = c(.001, .01, .05),insig = "label_sig",         method="color",type = "lower", col = colors, title = "Total grooming mixed")
```

Proximity
```{r - prox st bt trans ec,  fig.keep = 'last', echo=FALSE, warning=FALSE}
layout(t(1:2))

# prox st bt trans ec
stat7 <- all_prox_df_mixed %>%
  select(-chimp_id, -year, -sex) %>%
  cor(.,  method = "spearman", use = "pairwise.complete.obs") 
pmat7 <- all_prox_df_mixed %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(.,  method = "spearman", use = "pairwise.complete.obs") %>% .[[1]] 

colors <- colorRampPalette(c("blue", "white", "red"))(200)

corrplot(stat7, p.mat= pmat7, sig.level = c(.001, .01, .05),insig = "label_sig",         method="color",type = "lower", col = colors)

# prox st bt trans ec
stat8 <- all_prox_df_same %>%
  select(-chimp_id, -year, -sex) %>%
  cor(.,  method = "spearman", use = "pairwise.complete.obs") 
pmat8 <- all_prox_df_same %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(.,  method = "spearman", use = "pairwise.complete.obs") %>% .[[1]] 

colors <- colorRampPalette(c("blue", "white", "red"))(200)

corrplot(stat8, p.mat= pmat8, sig.level = c(.001, .01, .05),insig = "label_sig",         method="color",type = "lower", col = colors)

```

### Within individuals

Social animals may be observed more, but are animals more social when they’re observed more?

Number of subjects for within individual analysis.
```{r subjects for correlation , include = FALSE}
# subjects with >=3 year in study
rep <- dir_uw_df_mixed %>%
  count(chimp_id) %>%
  filter(n >= 3) %>%
  pull(chimp_id)
length(rep)

sex <- dir_uw_df_mixed %>%
  filter(chimp_id %in% rep) %>%
  distinct(chimp_id, sex) %>%
  pull(sex)
length(sex)
```

#### Mixed sex

**In-degree and out-degree - mixed sex**
```{r gm dir deg mixed, echo=FALSE, warning=FALSE}
stat <- vector("list", length = length(rep))
pval <- vector("list", length = length(rep))
data <- dir_uw_df_mixed
  
var_names <- data %>%
  select(-chimp_id, -year, -sex) %>%
  names()
sna_names <- var_names[!(var_names %in% c("focal_hours", "party_hours"))]


for(i in seq(rep)){
  
  corr_stat <- data %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor(., method = "spearman") %>%
  data.frame() %>%
  select(all_of(sna_names)) %>%
  rownames_to_column() %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)
# when sd is 0, NA produced for cor stat

  stat[[i]] <- data.frame(chimp_id = rep[i],sex = sex[i], corr_stat)
  
corr_pval <- data %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(., method = "spearman") %>%
  .[[1]] %>%
  data.frame() %>%
  set_names(., var_names) %>%
  select(all_of(sna_names)) %>%
  mutate(rowname = var_names) %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)  
  
  pval[[i]] <- data.frame(chimp_id = rep[i], sex = sex[i], corr_pval)

}

a1 <- do.call("rbind", stat) 
c1 <- a1 %>%
  summarise_if(is.numeric, list(avg_rho = mean, sd_rho = sd), na.rm = T) %>%
  t()


b1 <- do.call("rbind",pval) 
d1 <- b1 %>%
  summarise_if(is.numeric, list(avg_p = mean, sd_p = sd), na.rm = T) %>%
  t()

c1
d1
```
**In-strength and out-strength - mixed sex**
```{r gm dir st mixed, echo=FALSE, warning=FALSE}
stat <- vector("list", length = length(rep))
pval <- vector("list", length = length(rep))
data <- dir_w_df_mixed

var_names <- data %>%
  select(-chimp_id, -year, -sex) %>%
  names()
sna_names <- var_names[!(var_names %in% c("focal_hours", "party_hours"))]


for(i in seq(rep)){
  
  corr_stat <- data %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor(., method = "spearman", use = "pairwise.complete.obs") %>%
  data.frame() %>%
  select(all_of(sna_names)) %>%
  rownames_to_column() %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)
# when sd is 0, NA produced for cor stat

  stat[[i]] <- data.frame(chimp_id = rep[i], sex = sex[i], corr_stat)
  
corr_pval <- data %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(., method = "spearman", use = "pairwise.complete.obs") %>%
  .[[1]] %>%
  data.frame() %>%
  set_names(., var_names) %>%
  select(all_of(sna_names)) %>%
  mutate(rowname = var_names) %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)  
  
  pval[[i]] <- data.frame(chimp_id = rep[i], sex = sex[i], corr_pval)

}

a2 <- do.call("rbind", stat) 
c2 <- a2 %>%
  summarise_if(is.numeric, list(avg_rho = mean, sd_rho = sd), na.rm = T) %>%
  t()

b2 <- do.call("rbind",pval) 
d2 <- b2 %>%
  summarise_if(is.numeric, list(avg_p = mean, sd_p = sd), na.rm = T) %>%
  t()
c2
d2
```
**Grooming bt, trans, and ec - mixed sex**
```{r total gm mixed, echo=FALSE, warning=FALSE}
stat <- vector("list", length = length(rep))
pval <- vector("list", length = length(rep))
data <- other_gm_df_mixed 

var_names <- data %>%
  select(-chimp_id, -year, -sex) %>%
  names()
sna_names <- var_names[!(var_names %in% c("focal_hours", "party_hours"))]

for(i in seq(rep)){
  
  corr_stat <- data %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor(., method = "spearman", use = "pairwise.complete.obs") %>%
  data.frame() %>%
  select(all_of(sna_names)) %>%
  rownames_to_column() %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)
# when sd is 0, NA produced for cor stat

  stat[[i]] <- data.frame(chimp_id = rep[i], sex = sex[i], corr_stat)
  
corr_pval <- data %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(., method = "spearman", use = "pairwise.complete.obs") %>%
  .[[1]] %>%
  data.frame() %>%
  set_names(., var_names) %>%
  select(all_of(sna_names)) %>%
  mutate(rowname = var_names) %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)  
  
  pval[[i]] <- data.frame(chimp_id = rep[i], sex = sex[i], corr_pval)

}

a3<- do.call("rbind", stat) 
c3 <- a3 %>%
  summarise_if(is.numeric, list(avg_rho = mean, sd_rho = sd), na.rm = T) %>%
  t()

b3<-do.call("rbind",pval) 
d3 <- b3 %>%
  summarise_if(is.numeric, list(avg_p = mean, sd_p = sd), na.rm = T) %>%
  t()
c3
d3
```
**Prox st, bt, trans, and ec - mixed sex**
```{r prox mixed, echo=FALSE, warning=FALSE}
stat <- vector("list", length = length(rep))
pval <- vector("list", length = length(rep))
data <- all_prox_df_mixed

var_names <- data %>%
  select(-chimp_id, -year, -sex) %>%
  names()
sna_names <- var_names[!(var_names %in% c("focal_hours", "party_hours"))]

for(i in seq(rep)){
  
  corr_stat <- data %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor(., method = "spearman", use = "pairwise.complete.obs") %>%
  data.frame() %>%
  select(all_of(sna_names)) %>%
  rownames_to_column() %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)
# when sd is 0, NA produced for cor stat

  stat[[i]] <- data.frame(chimp_id = rep[i], sex = sex[i], corr_stat)
  
corr_pval <- data %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(., method = "spearman", use = "pairwise.complete.obs") %>%
  .[[1]] %>%
  data.frame() %>%
  set_names(., var_names) %>%
  select(all_of(sna_names)) %>%
  mutate(rowname = var_names) %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)  
  
  pval[[i]] <- data.frame(chimp_id = rep[i], sex = sex[i], corr_pval)

}

a4<- do.call("rbind", stat) 
c4 <- a4%>%
  summarise_if(is.numeric, list(avg_rho = mean, sd_rho = sd), na.rm = T) %>%
  t()

b4<-do.call("rbind",pval) 
d4 <- b4 %>%
  summarise_if(is.numeric, list(avg_p = mean, sd_p = sd), na.rm = T) %>%
  t()
c4
d4

```

#### Same sex

**In-degree and out-degree - same sex**
```{r gm dir deg same, echo=FALSE, warning = FALSE}

stat <- vector("list", length = length(rep))
pval <- vector("list", length = length(rep))
data <- dir_uw_df_same

var_names <- dir_uw_df_same %>%
  select(-chimp_id, -year, -sex) %>%
  names()
sna_names <- var_names[!(var_names %in% c("focal_hours", "party_hours"))]


for(i in seq(rep)){
  
  corr_stat <- data %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor(., method = "spearman", use = "pairwise.complete.obs") %>%
  data.frame() %>%
  select(all_of(sna_names)) %>%
  rownames_to_column() %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)
# when sd is 0, NA produced for cor stat

  stat[[i]] <- data.frame(chimp_id = rep[i], sex = sex[i], corr_stat)
  
corr_pval <- data %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(., method = "spearman", use = "pairwise.complete.obs") %>%
  .[[1]] %>%
  data.frame() %>%
  set_names(., var_names) %>%
  select(all_of(sna_names)) %>%
  mutate(rowname = var_names) %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)  
  
  pval[[i]] <- data.frame(chimp_id = rep[i],sex =sex[i], corr_pval)

}

a5 <-do.call("rbind", stat) 
c5 <- a5 %>%
  summarise_if(is.numeric, list(avg_rho = mean, sd_rho = sd), na.rm = T) %>%
  t()

b5<-do.call("rbind",pval)
d5 <- b5 %>%
  summarise_if(is.numeric, list(avg_p = mean, sd_p = sd), na.rm = T) %>%
  t()
c5
d5
```
**In-strength and out-strength - same sex**
```{r gm dir st same, echo=FALSE, warning = FALSE}

stat <- vector("list", length = length(rep))
pval <- vector("list", length = length(rep))

var_names <- dir_w_df_same %>%
  select(-chimp_id, -year, -sex) %>%
  names()
sna_names <- var_names[!(var_names %in% c("focal_hours", "party_hours"))]


for(i in seq(rep)){
  
  corr_stat <- dir_w_df_same %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor(., method = "spearman", use = "pairwise.complete.obs") %>%
  data.frame() %>%
  select(all_of(sna_names)) %>%
  rownames_to_column() %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)
# when sd is 0, NA produced for cor stat

  stat[[i]] <- data.frame(chimp_id = rep[i], sex = sex[i], corr_stat)
  
corr_pval <- dir_w_df_same %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(., method = "spearman", use = "pairwise.complete.obs") %>%
  .[[1]] %>%
  data.frame() %>%
  set_names(., var_names) %>%
  select(all_of(sna_names)) %>%
  mutate(rowname = var_names) %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)  
  
  pval[[i]] <- data.frame(chimp_id = rep[i], sex = sex[i], corr_pval)

}

a6<-do.call("rbind", stat) 
c6 <- a6 %>%
  summarise_if(is.numeric, list(avg_rho = mean, sd_rho = sd), na.rm = T) %>%
  t()

b6<-do.call("rbind",pval) 
d6<- b6 %>%
  summarise_if(is.numeric, list(avg_p = mean, sd_p = sd), na.rm = T) %>%
  t()
c6
d6

```
**Grooming bt, trans, and ec - same sex**
```{r total gm same, echo=FALSE, warning=FALSE}
stat <- vector("list", length = length(rep))
pval <- vector("list", length = length(rep))
data <- other_gm_df_same 

var_names <- data %>%
  select(-chimp_id, -year, -sex) %>%
  names()
sna_names <- var_names[!(var_names %in% c("focal_hours", "party_hours"))]

for(i in seq(rep)){
  
  corr_stat <- data %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor(., method = "spearman", use = "pairwise.complete.obs") %>%
  data.frame() %>%
  select(all_of(sna_names)) %>%
  rownames_to_column() %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)
# when sd is 0, NA produced for cor stat

  stat[[i]] <- data.frame(chimp_id = rep[i], sex = sex[i], corr_stat)
  
corr_pval <- data %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(., method = "spearman") %>%
  .[[1]] %>%
  data.frame() %>%
  set_names(., var_names) %>%
  select(all_of(sna_names)) %>%
  mutate(rowname = var_names) %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)  
  
  pval[[i]] <- data.frame(chimp_id = rep[i], sex = sex[i], corr_pval)

}

a7 <- do.call("rbind", stat)
c7 <- a7 %>%
  summarise_if(is.numeric, list(avg_rho = mean, sd_rho = sd), na.rm = T) %>%
  t()

b7 <- do.call("rbind",pval) 
d7 <- b7 %>%
  summarise_if(is.numeric, list(avg_p = mean, sd_p = sd), na.rm = T) %>%
  t()
c7
d7
```
**Prox st, bt, trans, and ec - same sex**
```{r prox same, echo=FALSE, warning=FALSE}
stat <- vector("list", length = length(rep))
pval <- vector("list", length = length(rep))
data <- all_prox_df_same

var_names <- data %>%
  select(-chimp_id, -year, -sex) %>%
  names()
sna_names <- var_names[!(var_names %in% c("focal_hours", "party_hours"))]

for(i in seq(rep)){
  
  corr_stat <- data %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor(., method = "spearman", use = "pairwise.complete.obs") %>%
  data.frame() %>%
  select(all_of(sna_names)) %>%
  rownames_to_column() %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)
# when sd is 0, NA produced for cor stat

  stat[[i]] <- data.frame(chimp_id = rep[i], sex = sex[i], corr_stat)
  
corr_pval <- data %>%
  filter(chimp_id == rep[i]) %>%
  select(-chimp_id, -year, -sex) %>%
  cor.mtest(., method = "spearman", use = "pairwise.complete.obs") %>%
  .[[1]] %>%
  data.frame() %>%
  set_names(., var_names) %>%
  select(all_of(sna_names)) %>%
  mutate(rowname = var_names) %>%
  filter(rowname %in% c("focal_hours", "party_hours")) %>% 
  pivot_wider(names_from = rowname, values_from = sna_names)  
  
  pval[[i]] <- data.frame(chimp_id = rep[i], sex = sex[i], corr_pval)

}

a8<- do.call("rbind", stat) 
c8 <- a8 %>%
  summarise_if(is.numeric, list(avg_rho = mean, sd_rho = sd), na.rm = T) %>%
  t()

b8<-do.call("rbind",pval) 
d8 <- b8 %>%
  summarise_if(is.numeric, list(avg_p = mean, sd_p = sd), na.rm = T) %>%
  t()
c8
d8
```

**By sex within individual correlations of SNA by obs**
```{r sna by obs rho and p averages by sex, echo = FALSE}
r_rhos <- mget(paste0(rep("a",8), seq(1:8))) %>% bind_rows()
#WHY NAs in by sex summaries?
r_rhos %>%
  filter(is.na(sex))
r_rhos %>%
  select(-chimp_id) %>%
  group_by(sex) %>%
  summarise_all(list(avg_rho =  mean, sd_rho = sd), na.rm = T)

r_ps <- mget(paste0(rep("b",8), seq(1:8))) %>% bind_rows()
r_ps %>%
  group_by(sex) %>%
  summarise_if(is.numeric, list(avg_p = mean, sd_p = sd), na.rm = T)
```


###### Max min within individual rho's and p's
**max and min average rho's and p's**
```{r range of by measure avg rhos, echo = FALSE}
rhos <- unlist(mget(paste0(rep("c",6), c(1:3,5:7)))) # skipping prox
data.frame(max = max(rhos), min = min(rhos), avg = mean(rhos))

```

```{r range of by measure avg ps, echo = FALSE}
ps <- unlist(mget(paste0(rep("d",6), c(1:3,5:7)))) # skipping prox
data.frame(max = max(ps), min = min(ps), avg = mean(ps))
```

**max and min raw rho's and p's**
```{r range of by individual rhos, echo = FALSE}
r_rhos <- mget(paste0(rep("a",8), seq(1:8))) %>% bind_rows()
r_rhos %>%
  select(-chimp_id, - sex) %>%
  summarise_all(list(min = min, max = max), na.rm = T)
  

```

```{r range of by individual ps, echo = FALSE}
r_ps <- mget(paste0(rep("b",8), seq(1:8))) %>% bind_rows()
r_ps %>%
  select(-chimp_id, -sex) %>%
  summarise_all(list(avg = mean, min = min, max = max), na.rm = T) %>%
  t()

```




